Estimating duration in the presence of misclassification

### 2024-08-17 cis-imperfect-testing.tex
proof read corrections

Introducing false negatives means that $O(j)$, containing the test results which would bound the length of episode $j$ in the absence of false negatives, is a random variable even after conditioning on $B_j$ and $E_j$.
Therefore, the results between the tests that bound episode $j$'s beginning and end times should now enter into the likelihood.
For tractability, I consider only tests between the negative tests providing an upper bound on the length of episode $j$.

>>>>

Recall that, for an undetected infection episode, $O(j) = \emptyset$ and, for a detected episode, $O(j) = [l_j^{(b)}, r_j^{(b)}, l_j^{(e)}, r_j^{(e)}, i(j)]^T$ where $r_j^{(b)}$ is the day of the first positive due to infection episode $j$; $l_j^{(b)}$ is the day after the negative preceding this positive; $l_j^{(e)}$ is the day of the final positive due to infection episode $j$; $r_j^{(e)}$ is the day before the negative test following this positive; and $i(j)$ is the individual episode $j$ occurred in.
As $O(j)$ contains test results now subject to false negatives, it is now a random variable even after conditioning on $B_j$ and $E_j$ (previously it was deterministic).
Additionally, the results between the tests that bound episode $j$'s beginning and end times are also random and hence should enter into the likelihood.
For tractability, I consider only tests between the negative tests providing an upper bound on the length of episode $j$.

### 2024-08-17 cis-perfect-testing.tex
proof read corrections

For our purposes, the $j$th infection episode ($j = 1, \dots, \ntot$) is $W_j = [B_j, E_j, i(j)]^T$ where $\ntot$ is the total number of infection episodes in the cohort; $i(j)$ is the individual the infection episode occurs in; $B_j$ is the day the episode begins (the first day $i(j)$ is detectable due to this infection episode); and $E_j$ is the day the episode ends (the last day $i(j)$ is detectable due to this infection episode).
The episode's duration is a deterministic transformation of these variables, $D_j = E_j - B_j + 1$; and I assume that $B_j$, $D_j$, and $i(j)$ are independent.
$D_j$'s distribution is determined by $\vec{\theta}$; both $B_j$ and $i(j)$ have uniform distributions over their respective state spaces.

@@

A particular violation of independence is the household design of the CIS.
Individuals in the same household both have correlated infection times and correlated testing times, as they will typically have the same test schedule.
If the test schedules are truly uninformative, as assumed here, this is unlikely to introduce bias; however, further work is required to confirm this hypothesis.

>>>>

For our purposes, the $j$th infection episode ($j = 1, \dots, \ntot$) is $W_j = [B_j, E_j, i(j)]^T$ where $\ntot$ is the total number of infection episodes in the cohort; $i(j)$ is the individual the infection episode occurs in; $B_j$ is the day the episode begins (the first day $i(j)$ is detectable due to this infection episode); and $E_j$ is the day the episode ends (the last day $i(j)$ is detectable due to this infection episode).
The episode's duration is a deterministic transformation of these variables, $D_j = E_j - B_j + 1$; and I assume that $B_j$, $D_j$, and $i(j)$ are independent.
$D_j$'s distribution is determined by $\vec{\theta}$; both $B_j$ and $i(j)$ are modelled as draws from uniform distributions over their respective discrete state spaces.

@@

A particular violation of independence is the household design of the CIS.
Individuals in the same household have both correlated infection times and correlated testing times, as they will typically have the same test schedule.
If the test schedules are truly uninformative, as assumed here, this is unlikely to introduce bias; however, further work is required to confirm this hypothesis.

### 2024-08-17 conclusion.tex
Christl comment on representativeness
proof read corrections

Overall, I have found that representative prevalence surveys are a promising approach for pandemic surveillance.
A well-designed survey is sufficient to estimate incidence and transmission, although not currently the duration of detectability.

>>>>

Overall, I have found that gold-standard prevalence surveys are a promising approach for pandemic surveillance.
A well-designed survey alone can be used to estimate incidence and transmission, although not currently the duration of detectability.

### 2024-08-17 introduction.tex
proof read corrections

On 31 Dec 2019, China notified the WHO (World Health Organization) that they had detected several cases of pneumonia of unknown cause in Wuhan City, Hubei province~\autocite{whoNovelPneumonia2020}.
By 7 Jan 2020, the cause of the pneumonia had been identified as a novel coronavirus which would go on to be named SARS-CoV-2~\autocite{whoNovelCov2020}.
SARS-CoV-2 spread rapidly around the world: on 31 Jan 2020 the first cases were confirmed in England in two Chinese nationals~\autocite{bbcFirstUKCOVID}.
However, introductions from Spain and France in Mar 2020 were the most important sources of the epidemic in England~\autocite{duplessisEstablishment}.

@@

The response to the SARS-CoV-2 pandemic in the UK has been unprecedented, both in terms of the scientific input to policy and the surveillance data made available.
The most prominent surveillance outputs were produced by members of SPI-M-O (the Scientific Pandemic Influenza Group on Modelling Operational sub-group), a sub-committee of SAGE (the Scientific Advisory Group for Emergencies)~\autocite{medleySPIM,govSPIMO}.
SPI-M-O produced weekly estimates of the current state of the epidemic (\eg the value of $\Re$), known as \emph{nowcasting}.
The committee peer-reviewed these estimates to provide quality assurance and formed a consensus value using a statistical combination of the estimates~\autocite{parkCombining}.
The consensus value was published on the Government's website and informed its response to the pandemic~\autocite{govRnumber}.

@@

The extraordinary impact of SARS-CoV-2 led the UK Government to fund two large prevalence surveys which aimed to recruit representative samples of the general population; such surveys are considered the gold-standard for conducting population surveillance~\autocite{mccabeCISincidence}.
To achieve this aim, they invited individuals selected at random from the population; however, not all individuals selected responded to the invite introducing some non-representativeness (see \cref{E-biology-data:sec:MRP}).
These designs aim to avoid the biases of community testing and observe the general population.
These surveys use RT-PCR (Reverse Transcription Polymerase Chain Reaction, described in detail in \cref{E-biology-data:sec:PCR}) testing to detect the presence of the virus in a swab from an individual.
The first survey was the CIS (Coronavirus (COVID-19) Infection Survey), run by the ONS (Office for National Statistics)~\autocite{CIS,cisMethodsONS}.
The CIS was a longitudinal, household-based study, testing a large number of individuals weekly or monthly for SARS-CoV-2 infection (see \cref{E-intro:sec:cis} for a detailed description).

>>>>

On 31 Dec 2019, China notified the WHO (World Health Organization) that they had detected several cases of pneumonia of unknown cause in Wuhan City, Hubei province~\autocite{whoNovelPneumonia2020}.
By 7 Jan 2020, the cause of the pneumonia had been identified as a novel coronavirus which would go on to be named SARS-CoV-2~\autocite{whoNovelCov2020}.
SARS-CoV-2 spread rapidly around the world: on 31 Jan 2020 the UK government announced that the first two cases had been confirmed in England~\autocite{bbcFirstUKCOVID}.
However, introductions from Spain and France in Mar 2020 were the most important sources of the epidemic in England~\autocite{duplessisEstablishment}.

@@

The response to the SARS-CoV-2 pandemic in the UK was unprecedented, both in terms of the scientific input to policy and the surveillance data made available.
The most prominent surveillance outputs were produced by members of SPI-M-O (the Scientific Pandemic Influenza Group on Modelling Operational sub-group), a sub-committee of SAGE (the Scientific Advisory Group for Emergencies)~\autocite{medleySPIM,govSPIMO}.
SPI-M-O produced weekly estimates of the current state of the epidemic (\eg the value of $\Re$), known as \emph{nowcasting}.
The committee peer-reviewed these estimates to provide quality assurance and formed a consensus value using a statistical combination of the estimates~\autocite{parkCombining}.
The consensus value was published on the Government's website and informed its response to the pandemic~\autocite{govRnumber}.

@@

The extraordinary impact of SARS-CoV-2 led the UK Government to fund two large prevalence surveys which aimed to recruit representative samples of the general population; such surveys are considered the gold-standard for conducting population surveillance~\autocite{mccabeCISincidence}.
To achieve this aim, they invited participants who were randomly selected from the population; however, not all individuals selected responded to the invite and consented to participate; this introduced some non-representativeness (see \cref{E-biology-data:sec:MRP}).
These designs aim to avoid the biases of community testing.
These surveys use RT-PCR (Reverse Transcription Polymerase Chain Reaction, described in detail in \cref{E-biology-data:sec:PCR}) testing to detect the presence of the virus in a swab from an individual.
The first survey was the CIS (Coronavirus (COVID-19) Infection Survey), run by the ONS (Office for National Statistics)~\autocite{CIS,cisMethodsONS}.
The CIS was a longitudinal, household-based study, testing a large number of individuals weekly or monthly for SARS-CoV-2 infection (see \cref{E-intro:sec:cis} for a detailed description).
